Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-13 reply_to_referee.tex

The content of this reply is supplemented in App. C. We request the referee to reconsider the presented arguments.
}

(2) I also find the whole presentation of the mapping unsatisfactory. In part, this has to with the fact that no lengths are indicated in the figures.

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $\xi = 1$. To evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_\xi$. This should avoid the problem the referee was worried about.

@@

(We add the semi-circle manually in the center of Fig. 5, which is incidentally in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are not strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (which the referee maybe worried about), we notice the following fact
\begin{itemize}
\item the conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis. 
\end{itemize}
Since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

@@

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line should not matter. We therefore take the simplest periodic boundary condition for the ease of computation.

@@

- The system sizes in the numerics given in the captions are unclear to me. What does 30k or 35k mean? In Fig. 7, it says k=1 immediately after that. Is this the same k? If not, what is it? As with L, I think that such numbers should also appear in the text. If one is talking about 35.000 sites, one wonders why such a large number was taken.

\reply{The k in the math mode font is the spring constant, while the $k$ after 30 and 35 means 1000. We didn't realize the conflict. We have changed 30k to 30000 and 35k to 35000. We take 35000 sites for reducing the finite size effect in Fig. 8 which is important for the theta value near zero. }

- Fig. 11 corresponds to the right piece of Fig. 6, but is rotated by 90¬∞. This is confusing, in particular since the corresponding Fig. 12 is not rotated. The lambda line on the left has to be dotted. Also confusing is the use of x and L in (E1) below.

\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{\pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{\pi}$. }

### 2017-10-13 analy_eval.tex
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence. The introduction of regulators is also physically sensible when considering the lattice realization of the systems.

@@

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle around $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
\label{eq:partition_fun}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}

The height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$. So the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
\end{equation}

@@

The height of the cylinder is still $\pi$ because of folding. In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$. The end points of the larger semi-circle are at $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.

The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order. Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
\end{equation}
Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choice of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

@@

The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
\begin{equation}
\begin{aligned}
  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
\begin{pmatrix}
  \vec{{b}_1}\\
  \vec{{b}_2}
\end{pmatrix}\\
 &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
\end{aligned}
\end{equation}
where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
\end{equation}
The partition function is
\begin{equation}
\label{eq:Zab-bd}
\begin{aligned}
Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
\end{aligned}
\end{equation}

>>>>

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corners at the tip of the slits. Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence. The introduction of regulators is also physically sensible when considering the lattice realization of the systems.

@@

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle has coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot $\xi = 0$ corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that the only bcc operator on the real axis is the one enclosed by the blue semi-circle around $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
\label{eq:partition_fun}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}
where the height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ such that the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
\end{equation}

@@

The height of the cylinder is still $\pi$ because of folding. In the $\xi$ plane, the coordinates of the two end points of the small semi-circle are $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$, while those of the larger semi-circle are $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are gluing (open) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

\rev{Check this and the following paragraph} For the rest of this section, we should denote the width of the cylinder as $\beta$. After obtaining the partition function for the cylinder, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.

The actual boundary conditions on the blue lines, which are the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, are not important in the leading order. Taking Fig.~\ref{fig:fidel-map} for example, rather than using Eq.~\eqref{eq:partition_fun}, we can alternatively view the right panel as the amplitude between the two blue boundary states $|1\rangle$ and $|2\rangle$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  , 
\end{equation}
where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$. Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontally in this case) to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy reads
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choice of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

%Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.

%The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order. Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
%\begin{equation}
%Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
%\end{equation}
%Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
%\begin{equation}
%\begin{aligned}
%F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
%&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
%\end{aligned}
%\end{equation}
%where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choice of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

@@

The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
\begin{equation}
\begin{aligned}
  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
\begin{pmatrix}
  \vec{{b}_1}\\
  \vec{{b}_2}
\end{pmatrix}\\
 &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
\end{aligned}
\end{equation}
where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
\end{equation}
The partition function in Eq.~\eqref{eq:partition_fun} becomes
\begin{equation}
\label{eq:Zab-bd}
\begin{aligned}
Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
\end{aligned}
\end{equation}

### 2017-10-13 general_formulation.tex
[referee] 2nd round pass
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.

If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an identity for the boson creation and annihilation operators. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{eqnarray}\begin{aligned}
\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
 \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
\end{aligned}\end{eqnarray}
where we take the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} },
\end{equation}
with $T$ being the time period. We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
\end{aligned}
\end{equation}
which is valid for the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle,
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

@@

So far the deviation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''. For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$. Because the winding mode lives on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$. App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$. For example, the $S_1(\theta)$ interface should satisfy
\begin{equation}
\lambda = \tan \theta = \frac{n_2 R_1}{n_1 R_2}
\end{equation}
for coprime integer $n_1$ and $n_2$. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the CFTs on both sides.

>>>>

If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an identity for the boson creation and annihilation operators. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\label{eq:di_mode_expansion}
\begin{aligned}
\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
 \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
\end{aligned}
\end{equation}
where we take the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} },
\end{equation}
with $T$ being the time period. We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
\end{aligned}
\end{equation}
which is valid for the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle,
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

@@

So far the derivation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''. For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$. Because the winding modes live on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$. App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$. For example, the $S_1(\theta)$ interface should satisfy
\begin{equation}
\lambda = \tan \theta = \frac{n_2 R_1}{n_1 R_2}
\end{equation}
for coprime integer $n_1$ and $n_2$. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the CFTs on both sides.
